Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-08-19 review_article.Rmd
Cancer atlases in literature

<!-- what is a choropleth map -->
A choropleth map is used to display the characteristics of a spatial relationship of measurements. 
A choropleth map is a true map of the topology, constructed for visual inspection of spatial patterns on a familiar geographic form. 
Figure \ref{fig:choro} shows a choropleth map where each state of the United States of America is coloured by the average annual rate of new cases of lung and bronchus cancer from years 2012 to 2016.
Identifying and explaining spatial structures, patterns, and processes involves considering the individuals in communities and organising communities into representable units [@SAMGIS]. 
A choropleth is constructed by drawing the geographic or political boundaries, and filling the shapes with colours to represent values of a measured variable [@EI].
Early versions of choropleth maps used symbols or patterns instead of colour.
As an alternative storage device to a table, it preserves locations for geographically ordered data, with usage dating back to the 1800s [@GOINO].
@CPISACA discuss the use of choropleths to visualise cancer data, and @DMAHP gives an overview of the development of these maps for displaying disease data.

@@

The presentation of these rates considered not only the map base, but also appropriate choices of colour blind friendly colour schemes, and categories of the values to highlight signifcantly different areas.

<!--

>>>>

<!-- what is a choropleth map -->
A choropleth map is used to display the characteristics of a spatial relationship of measurements. 
A choropleth map is a true map of the topology, constructed for visual inspection of spatial patterns on a familiar geographic form. 
Figure 1 shows a choropleth map where each state of the United States of America is coloured by the average annual rate of new cases of lung and bronchus cancer from years 2012 to 2016.
Identifying and explaining spatial structures, patterns, and processes involves considering the individuals in communities and organising communities into representable units [@SAMGIS]. 
A choropleth is constructed by drawing the geographic or political boundaries, and filling the shapes with colours to represent values of a measured variable [@EI].
Early versions of choropleth maps used symbols or patterns instead of colour.
As an alternative storage device to a table, it preserves locations for geographically ordered data, with usage dating back to the 1800s [@GOINO].
@CPISACA discuss the use of choropleths to visualise cancer data, and @DMAHP gives an overview of the development of these maps for displaying disease data.

@@

The presentation of these rates considered not only the map base, but also appropriate choices of colour blind friendly colour schemes, and categories of the values to highlight signifcantly different areas.
<!--
